Robots, Are They Overlords or Serf-Laborers?

### 2015-06-09 draft1.tex
Add a page break between old and new paper
Start to merge two paper in a logical sequence

\section{New Synthesis}
\citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
Even though the term robot was coined two centuries ago and the idea of (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of AI.\par
By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this slave-like definition has altered to something brand new as technology advances. In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics. These two definitions emphasize different aspect of Robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition. Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible. The second definition, however, takes autonomy into account. A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment. In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions. However, \citeA{lan} asserts that socially interaction robots are significantly popular among society. Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized. This discrepancy brings about a major problem in individual and societal level. For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man. Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot. Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue. The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients. However, these two prominent terms of technology closely resembles another, the Internet. As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.

@@

Although AI is a research topic in the fields of engineering and science, the first introduction of it was fictional literary and futuristic artistic works. For that reason, its popularity significantly
ascended which resulted in becoming perhaps the most debated technology related term in the last century. Despite AI's popularity, it may be the most misunderstood term that in the field of engineering. In order to make clear its obfuscated definition, the tasks of AI should be mentioned. The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion. The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making. Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par

@@

@@

The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more
sophisticated hardware was developed. For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}. The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology. Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation. The other issue precluding the creation of AI is the challenges of information collection. As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI. For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research. Another example of the imitation of humanistic features is the structure of the human brain. The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has
enabled researchers to achieve more in the creation of AI. 

@@

Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term. Consequently, second generations robots created by the first generations would be utterly
dependent on the first generation robots which means the first generation robots might command their offspring how ever they want. This unpredictable action-decision chain raises a major security problems including human annihilation for the society. 

@@

In addition to former arguments, \citeA{rosa} proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession
from the one that it had been taught or coded to a brand new one. This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.

@@

\section{Conclusion}
As the research studies toward the creation of AI deepens, this technological advancements will raise more ethical problems. Regardless of the sources of issues, these problems relate to AI's definition and its responsibilities. It is crucially important to decide whether or not robots are simply functional machine that is utilitarian in its responsibilities and nothing more. If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code. However, the results of recent studies indicate that in near future individuals may possess personal robots interacting closely with their master. In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention. If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots, which are closely related to the terms of AI, will also evolve rapidly to its excellence. The only limitation in its experimental progress should be the initial motivations which must permanently coded to create anti-behaviors constraining its action-decision chain.
\bibliographystyle{apacite}
\bibliography{bibliography}
\end{document}

>>>>

% Citing examples \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}

@@

\subsection{v1}
Although AI is a research topic in the fields of engineering and science, the first introduction of it was fictional literary and futuristic artistic works. For that reason, its popularity significantly ascended which resulted in becoming perhaps the most debated technology related term in the last century. Despite AI's popularity, it may be the most misunderstood term that in the field of engineering. In order to make clear its obfuscated definition, the tasks of AI should be mentioned. The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion. The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making. Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par

@@

\subsection{v2}
Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level.\par
Formation (As it follows: \#\#, \#\#, \#\#)

@@

The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more sophisticated hardware was developed. For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}. The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology. Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation. The other issue precluding the creation of AI is the challenges of information collection. As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI. For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research. Another example of the imitation of humanistic features is the structure of the human brain. The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has enabled researchers to achieve more in the creation of AI.

@@

Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term. Consequently, second generations robots created by the first generations would be utterly dependent on the first generation robots which means the first generation robots might command their offspring how ever they want. This unpredictable action-decision chain raises a major security problems including human annihilation for the society. 

@@

In addition to former arguments, \citeA{rosa} proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one. This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.

@@

\section{The Bigger Picture}
\subsection{What is a Robot?}
By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this slave-like definition has altered to something brand new as technology advances. In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics. These two definitions emphasize different aspect of Robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition. Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.
The second definition, however, takes autonomy into account. A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment. In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions. However, \citeA{lan} asserts that socially interaction robots are significantly popular among society. Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized. This discrepancy brings about a major problem in individual and societal level. For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man. Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
\subsection{What (should) does a Robot do?}
Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.
The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par

\section{Conclusion}
\subsection{v1}
As the research studies toward the creation of AI deepens, this technological advancements will raise more ethical problems. Regardless of the sources of issues, these problems relate to AI's definition and its responsibilities. It is crucially important to decide whether or not robots are simply functional machine that is utilitarian in its responsibilities and nothing more. If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code. However, the results of recent studies indicate that in near future individuals may possess personal robots interacting closely with their master. In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention. If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots, which are closely related to the terms of AI, will also evolve rapidly to its excellence. The only limitation in its experimental progress should be the initial motivations which must permanently coded to create anti-behaviors constraining its action-decision chain.
\subsection{v2}
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients. However, these two prominent terms of technology closely resembles another, the Internet. As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved. 
\bibliographystyle{apacite}
\bibliography{bibliography}
\end{document}
